Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-09 documentation/paper.tex
Cropped and renamed graph; explained grav diff a little better

@@

The essential purpose of $GravDiff(p, \psi, g)$ is to allow confidently classified unlabeled examples to influence the training process, pushing them further towards the classification they are already near (like gravity), while ensuring examples with low-confidence classifications do not have a significant adverse effect.

It can be considered a distortion of the hyperbolic tangent that flattens the central range and exaggerates the asymptote on either side. The network's prediction $p$ is first transformed so its range is 1 to -1 rather than 0 to 1 ($2(p - 0.5)$). Next, the sigmoidal hyperbolic tangent is applied, producing a value of 0 in the center and asymptotic slopes to -1 and 1 at the edges.

@@

>>>>

\subsubsection{Algorithm}

@@

The essential purpose of $GravDiff(p, \psi, g)$ is to allow confidently classified (near 0 or 1) unlabeled examples to influence the training process, pushing them further towards the classification they are already near (like gravity), while ensuring examples with low-confidence (near 0.5) classifications do not have a significant effect.

It is a distortion of the hyperbolic tangent that flattens the central range and comparatively exaggerates the asymptote on either side. The network's prediction $p$ is first transformed so its range is 1 to -1 rather than 0 to 1 ($2(p - 0.5)$). Next, the sigmoidal hyperbolic tangent is applied, producing a value of 0 in the center and asymptotic slopes to -1 and 1 at the edges.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_diff}
    \caption{\label{grav_diff} A visualization of $GravDiff(p, \psi, g)$ with respect to $p$ and $\psi$.}
\end{figure}

\subsubsection{Application}
